Single-cell virus sequencing of influenza infections that trigger innate immunity

### 2019-03-05 paper/paper.tex
revisions to `p_mutations` figure legend

%%% begin mutations figure %%%
\begin{figure}
\begin{fullwidth}
{\centering
\includegraphics[width=\linewidth]{figures/single_cell_figures/p_mutations.pdf}
}
\caption{
{\bf Viral features associated with heterogeneity in infection outcome among cells for which we sequenced all expressed viral genes.}
{\bf (A)} 
Percent of all mRNA derived from virus, faceted by whether cells express unmutated copies of all eight genes.
Cells infected by fully wild-type virus exhibit less heterogeneity in viral burden as quantified by the Gini index (95\% confidence intervals are indicated).
{\bf (B)}
IFN expression among cells expressing unmutated copies of all genes, and among cells with mutations or missing genes.
{\bf (C)}
Specific viral defects associated with IFN induction.
The top panel show the percent of IFN- and IFN+ cells that fail to express each viral gene.
The middle and bottom panels show the percent of IFN- and IFN+ cells that have a deletion or amino-acid substitution in each gene, conditioned on the cell expressing that gene.
Numbers give P-values (Fisher's exact test) for rejecting the null hypothesis that percents are equal among IFN- and IFN+ cells. 
{\bf (D)}
There is no association between IFN induction and the amount of viral mRNA in cells that express NS, but viral burden is associated with IFN induction among cells that lack NS.
Throughout this figure, we only consider substitutions that are non-synonymous.
Insertions are not shown as a mutation type as they are extremely rare (\FIG{genotypes}).
}
\label{fig:mutations}

>>>>

%%% begin mutations figure %%%
\begin{figure}
\begin{fullwidth}
{\centering
\includegraphics[width=\linewidth]{figures/single_cell_figures/p_mutations.pdf}
}
\caption{
{\bf Viral features associated with heterogeneity in infection outcome among cells for which we determined viral genotypes.}
{\bf (A)} 
Percent of all mRNA derived from virus, faceted by whether cells express unmutated copies of all eight genes.
Cells infected by fully unmutated virions exhibit less heterogeneity in viral burden as quantified by the Gini index (95\% confidence intervals are indicated).
{\bf (B)}
IFN expression among cells expressing unmutated copies of all genes, and cells with mutations or missing genes.
{\bf (C)}
Specific viral defects associated with IFN induction.
The top panel show the percent of IFN- and IFN+ cells that fail to express each viral gene.
The middle and bottom panels show the percent of IFN- and IFN+ cells with a deletion or amino-acid substitution in each gene, conditioned on the cell expressing that gene.
Numbers give P-values (Fisher's exact test) for rejecting the null hypothesis that percents are equal among IFN- and IFN+ cells. 
{\bf (D)}
There is no association between IFN induction and the amount of viral mRNA in cells that express NS, but viral burden is associated with IFN among cells that lack NS.
Throughout this figure, we only consider substitutions that are non-synonymous.
Insertions are not shown as a mutation type as they are extremely rare (\FIG{genotypes}).
}
\label{fig:mutations}
